### 2022-10-18 README.Rmd
Improved help on functions and more functions for comparing scenarios. No EWN.
Added doquantplot and finalcondyeardepletion functions. No EWN.
Altered projections to be all replicates by year rather than all years per replicate.

>>>>

* 2022-10-18 aMSE 0.0.18 In the projections relicates across years has now been changed to years across replicates to allow for inclusion of FIS performance measures. Also, further comparison functions included.

* 2022-09-26 aMSE 0.0.17 Added finalcondyeardepletion to aid in comparisons.

* 2022-08-24 aMSE 0.0.16 Started to add depensation and other refinements.
